Verifying Demonstrations

### 2019-10-16 paper/distance-bounding.tex
Writes up strSimTF definition

\daniel{The following definition differs slightly from that of 
  \textcite{FormalTerroristFraud}: we use \(m_{k'}\) instead of \(m_k'\).
  \Ie that the number of messages in \(\sid\) is not required to be the same 
  and in the same order as in \(\sid'\).}

\begin{definition}[Tainted session, \acs*{DBTF}]\label{TaintedTF}
  A time-critical round
  \(\Xscript{\sid}{k, k+1} = (m_k, m_{k+1})\)
  of an adversary--verifier session~\(\sid\), where \(m_k\) is sent by the 
  verifier, is \emph{tainted} by the round
  \(\Xscript{\sid'}{k', k'+1} = (m_{k'}, m_{k'+1})\)
  of a prover--adversary session~\(\sid'\) if
  \begin{align*}
    \marker[\sid, k] &< \marker[\sid', k'] \\
    \marker[\sid, k'+1] &> \marker[\sid', k'+1].
  \end{align*}
\end{definition}

\begin{definition}[strSimTF resistance~\cite{FormalTerroristFraud}]%
  \label{TFresistance}
  \dots
\end{definition}

>>>>

\begin{definition}[Tainted session, \acs*{DBTF} 
  (strSimTF)~\cite{FormalTerroristFraud}]\label{TaintedTF}
  A time-critical round
  \[\Xscript{\sid}{k, \dotsc, k+2l-1} = (m_k, \dotsc, m_{k+2l-1}),\] for 
  \(l\geq 1\), of an adversary--verifier session~\(\sid\), where \(m_k\) is 
  sent by the verifier, is \emph{tainted} by the round
  \[\Xscript{\sid'}{k, \dotsc, k+2l-1} = (m'_{k}, m'_{k+2l-1})\]
  of a prover--adversary session~\(\sid'\) if
  \begin{align*}
    \marker[\sid, k+2i] &< \marker[\sid', k+2i] \\
    \marker[\sid, k+2i+1] &> \marker[\sid', k+2i+1].
  \end{align*}
\end{definition}

Then we have the following definition of security.

\begin{definition}[SimTF security~\cite{DB-DFKO}]%
  \label{TFresistance}
  Let \(\DB\) be an authentication scheme for parameters \((t_{\max}, T_{\max}, 
    E_{\max}, N_c)\).
  Let \(\adv\) be a \((t, \qv, q_{\F})\)-SimTF adversary, \(\S\) an algorithm 
  with runtime \(t_{\S}\) and \(\F\) an algorithm with runtime \(t_{\F}\).
  Let \[
    \Adv_{\DB}^{\text{TF}}(\adv, \S, \F) = p_{\adv} - p_{\S},
  \] where \(p_{\adv}\) is the probability that the verifier~\(v\) accepts in 
  one of the \(\qv\) adversary--verifier sessions~\(\sid\) such that at 
  \(T_{\max}\) time-critical phases of \(\sid\) are tainted and \(p_{\S}\) is 
  the probability that, given the state of \(\adv\), \(\S\) authenticates to 
  the verifier~\(v\) in one of \(\qv\) subsequent executions.
\end{definition}
